Model

### 2019-04-26 stats/model.Rmd
test run hierarchical model

@@

```{r}
# me_model_data <- read_csv("../data/child_basic_me.csv")%>%
#     filter(trial != "train1",
#            trial != "train2")%>%
#   mutate(age = age_num - min(age_num))

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "incrementalMH", 
                        samples = 10, 
                        burn = 5,
                        verbose = T)#,
                        #verboseLag = 500)
)

#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
sem_know_model <- readRDS("../saves/sem_know_model.rds") %>%
  filter(Chain != 1)
```

@@

sem_know <- sem_know_model %>%
  filter(Parameter != "speaker_optimality") %>%
  mutate(Parameter = factor(Parameter)) %>%
  separate(value, into = c("intercept", "slope"), 
           sep = ", ") %>%
  mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]"))) %>%
  rename(item = Parameter) %>%
  gather(parameter, value, intercept, slope)

sem_know_params <- sem_know %>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

speak_opt <- sem_know_model %>%
  filter(Parameter == "speaker_optimality") %>%
  separate(value, into = c("intercept", "slope"), 
           sep = ", ")%>%
  mutate(intercept = as.numeric(str_remove_all(intercept, "[(c]")),
         slope = as.numeric(str_remove(slope, "[)]"))) %>%
  rename(item = Parameter) %>%
  gather(parameter, value, intercept, slope)

@@

```{r}
ggplot(sem_know, aes(x = value))+#, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~item, scales = 'free')+
  theme_few()
```

```{r}
ggplot(speak_opt, aes(value))+
  geom_density()+
  xlab("Parameter")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()
```

@@

inv_model_plot <- ggplot(inv_predictions, aes(x=age,y = me_effect, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Inverse Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()

>>>>

      display(age)

@@

```{r}
me_model_data <- read_csv("../data/child_basic_me.csv")%>%
    filter(trial != "train1",
           trial != "train2")%>%
  mutate(age = age_num - min(age_num))

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, semStr , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "incrementalMH", 
                        samples = 1, 
                        burn = 1,
                        verbose = T)#,
                        #verboseLag = 500)
)

#saveRDS(sem_know_model, "../saves/sem_know_model.rds")
#sem_know_model <- readRDS("../saves/sem_know_model.rds")
```

@@

model_pred <- sem_know_model %>%
  separate(Parameter, into = c("type", "token"))%>%
  filter(type == "modelPrediction")%>%
  separate(value, into = c("age", "pred"),sep = ", ")%>%
  mutate(age = as.numeric(str_remove_all(age, "[(c]")),
         pred = as.numeric(str_remove(pred, "[)]"))) %>%
  rename(item = token)

params<- sem_know_model %>%
  separate(Parameter, into = c("parameter", "type"), sep = ",")%>%
  filter(parameter == "parameter")%>%
  separate(value, into = c("slope", "int"),sep = ", ")%>%
  mutate(slope = as.numeric(str_remove_all(slope, "[(c]")),
         int = as.numeric(str_remove(int, "[)]")))%>%
  gather(parameter, value, int, slope)

sem_know_params <- params %>%
  filter(type != "speaker_optimality",
         type != "global_sem",
         type != "global_sem_sigmas")%>%
  rename(item = type)%>%
  group_by(item, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

global_params <- params %>%
  filter(type == "speaker_optimality" |
         type == "global_sem")%>%
  group_by(type, parameter)%>%
  summarise(mode = estimate_mode(value),
            uci = hdi_upper(value),
            lci = hdi_lower(value))

@@

```{r}
item_params <- params %>%
  filter(type != "speaker_optimality",
         type != "global_sem",
         type != "global_sem_sigmas")

ggplot(item_params, aes(x = value))+#, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~type, scales = 'free')+
  theme_few()
```

```{r}
param_params <- params %>%
  filter(type == "speaker_optimality" |
         type == "global_sem")

ggplot(param_params, aes(x = value))+#, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Parameter")+
  facet_grid(parameter~type, scales = 'free')+
  theme_few()
```

```{r}
sigma_params <- params %>%
  filter(type == "global_sem_sigmas")

ggplot(sigma_params, aes(x = value))+#, fill = factor(Chain)))+
  geom_density(alpha = 0.3)+
  xlab("Sigma")+
  facet_grid(~parameter, scales = 'free')+
  theme_few()
```

@@

inv_model_plot <- ggplot(model_pred, aes(x=age+2,y = pred, col = item))+
  geom_hline(yintercept = 0.5, lty=2)+
  geom_line(size = 1)+
  ggtitle("Inverse Model Predictions")+
  labs(x="Age",y="Proportion correct")+
  theme_few() +
  ylim(-0.05,1.05)+
  xlim(2,5)+
  guides(alpha = F)+ 
  scale_colour_viridis_d()
